\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.

@@

>>>>

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation.
Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x over other grasp evaluation methods.

@@

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a multi-armed bandit problem.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality under shape uncertainty represented as a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013} but has been limited by its computational complexity~\cite{rasmussen2006, williams2007}.
We also show how to estimate distributions on the contact points, surface normals, and center of mass using a GPIS shape representation and use those to efficiently sample from the GPIS for grasp quality evaluation, which reduces computational complexity of sampling from $O(n^6)$ to $O(n^3)$ for a 2D $n \times n$ workspace. Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of N grasps by T over other grasp evaluation methods.
